My title

### 2024-03-19 paper/paper.qmd
updating models and graphs

library(tidyverse)
library(palmerpenguins)
library(ggplot2)
library(rstanarm)
library(purrr)
library(kableExtra)

@@

```{r}
#| label: fig-1
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-2
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

@@

@@

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

@@

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

@@

```{r}
#| eval: false
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

@@

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

@@

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

@@

plot(first_model, "rhat")
```

>>>>

library(tidyverse)
library(palmerpenguins)
library(ggplot2)
library(rstanarm)
library(purrr)
library(kableExtra)
library(wesanderson)
library(viridis)
library(gridExtra)

@@

```{r}
#| label: fig-1
#| fig-cap: Levels of real disposable income, in billions of dollars, chained to 2017 prices
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-2
#| fig-cap: Levels of real consumption expenditure, in billions of dollars, chained to 2017 prices
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-3
#| fig-cap: Expenditure for different categories, in billions of 2017 dollars
#| echo: false
#| warning: false
#| message: false

data$date <- as.Date(data$date)

data_long <- reshape2::melt(data, id.vars = "date")

newnames <- c("durable_expenditure" = "Durable goods",
              "nondurable_expenditure" = "Nondurable goods",
              "food_expenditure" = "Food",
              "income_expenditure" = "Disposable income",
              "healthcare_expenditure" = "Halthcare",
              "services_expenditure" = "Services")

col <- viridis(6)

figure <- data_long |>
  ggplot( aes(x = date, y = value, fill = variable)) +
  geom_area() +
  labs(title = "Contribution of Expenditure Categories Over Time",
       x = "Date",
       y = "Expenditure",
       fill = "Categories") +
  theme_minimal() +
  scale_fill_manual(values = col, labels = newnames, name = "Categories")

print(figure)

@@

```{r}
#| label: fig-4
#| fig-cap: Relationship between increases in disposable income and increases in food expenditure, between 2007 and 2022.
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: tbl-3
#| tbl-cap: Summary results for both models

first_model <- 
  readRDS(file = here::here("models/model_1.rds"))

second_model <- 
  readRDS(file = here::here("models/model_2.rds"))

modelsummary::modelsummary(
  list(
    "First Model" = first_model,
    "Second Model" = second_model
  ),
  statistic = "mad",
  fmt = 2
)
```

@@

@@

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-5
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check of first model", "Posterior prediction check of second model"]

@@

pp_check(second_model) +
  theme_classic() +
  theme(legend.position = "bottom")

@@

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-6
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot of Model 1", "Trace plot of model 2"]
#| layout-ncol: 2

@@

plot(second_model, "trace")
